---
title: "Assignment3"
author: "Chaoying Chen"
date: "2/28/2022"
output: html_document
---

```{r }
library(caret)
library(class)
library(e1071)
library(gmodels)
library(e1071)
UB<-read.csv("UniversalBank.csv")
summary(UB)
```

```{r}
data<-UB[,c(13,14,10)]
#str(data)
data$Personal.Loan<-as.factor(data$Personal.Loan)
data$Online<-as.factor(data$Online)
data$CreditCard<-as.factor(data$CreditCard)
set.seed(123)
TrainUB<-createDataPartition(data$Personal.Loan,p=0.6,list = FALSE)
Tdata<-data[TrainUB,]
Vdata<-data[-TrainUB,]
mytable<-xtabs(~Tdata$CreditCard+Tdata$Personal.Loan+Tdata$Online, data=Tdata) 
ftable(mytable)  
```
The amount of people who accepts the loan is 51. The amount of people who has Credit Cards and is active in online service is 467+51. So the  probability that this customer will accept the loan offer is 0.0985.
##Create two separate pivot tables for the training data. 
```{r}
table(Personal.Loan=Tdata$Personal.Loan, Online=Tdata$Online)
table(Personal.Loan=Tdata$Personal.Loan, CreditCard=Tdata$CreditCard)
```
##Compute the following quantities 

i. P(CC = 1 | Loan = 1) =84/(204+84)=0.2916

ii. P(Online = 1 | Loan = 1)=176/(176+112)=0.6111

iii. P(Loan = 1) (the proportion of loan acceptors)= (112+176)/3000=0.096

iv. P(CC = 1 | Loan = 0)=777/(1935+777)=0.2865 

v. P(Online = 1 | Loan = 0) =1611/(1611+1101)=0.5940

vi. P(Loan = 0) =1-0.096=0.904

##E
P(Loan = 1 | CC = 1, Online = 1)

=[P(CC=1|Loan=1)P(Online=1|Loan=1)P(Loan=1)]/P(CC=1,Online=1)

=(0.2916*0.6111*0.096)/(((777+84)/3000)*((1611+176)/3000))

=0.100

##F
I think that the probability of calculating directly is more accurate than Bayes.

##G
```{r}
nb.model<-naiveBayes (data$Personal.Loan~data$CreditCard+data$Online, data=Tdata) 
To_Predict=data.frame(CreditCard='Yes', Online='Yes') 
predict(nb.model,To_Predict,type='raw')
```
The probability is 0.096.These two answers are very similiar.